Anomaly detection with kernel density estimation on manifolds

### 2022-04-11 paper/paper.Rmd
Move Riemmanian geometry to appendix

# Notions about Riemannian geometry {#riemgeo}

In this section, we present some notions about the Riemannian geometry used in this paper.

@@

>>>>

@@

\clearpage\appendix
\section{Appendix: Notions about Riemannian geometry}\label{riemgeo}
<!-- %\pagenumbering{arabic} -->
<!-- %\def\thepage{A\arabic{page}} -->

<!-- # Notions about Riemannian geometry {#riemgeo} -->

In this appendix, we present some notions about the Riemannian geometry used in this paper.
